The paper on \Large \bf Blockchain Frontrunning

### 2018-09-17 frontrunning/Latex/sections/paper.tex
[frontrunning] edits till 4.2

\subsection{Blockchain Front-running} % for the unity of the paper, the previous title : How are Blockchain Applications Vulnerable to Front-running? is changed to "Blokcchain front-running", in this case the other section's name (on blockchain frontrunning, where we talk about miner and non miner frontrunning) needs to change to sth different and more descriptive.
\label{sec:Front Running on the Blockchains}

@@

As mentioned in the Section~\ref{sec:intro}, for the purpose of this research we retrieved the top 25 DApps based on recent user activities from \footnote{List of decentralized applications \url{https://dappradar.com/dapps}} in the first week of September 2018. We then categorize these applications into 4 principal groups of decentral applications (see Table~\ref{tab:top25dapps}). In this section, we take a deep look into one or two decentral applications from each category and pinpoint the technical details of front-running issue on each case. Although, no ICOs were spot in the list at the time it was retrieved, we will thoroughly discuss our analysis on how ICOs are highly vulnerable to front-running activities (see Section~\ref{sec:ICOsfrontrunning}).

@@

% everything that has a line up , someone can jump in the line and front-run
% talk about velocity that seems to be not front-runnable but because of of the liquidity pool limitation, there can be an order that consumes the last chunk of liquidity "edge case" , to front run others and make their "option calls" fail

@@

% maybe inlcude 0xbitcoin ERC721 mineable tokens front-running!
% mint: https://etherscan.io/tx/0x9883bc3ad018fd2b649982f88fbad7dc5abcb8f11c4f1d87ef814ba30c2b3428
%______________________________________________________________%
\subsection{Markets and Exchanges.} \label{sec:frontrunningExchanges}

Exchanges such as EtherDelta\footnote{also known as ForkDelta for the UI \url{https://forkdelta.app/}}, are closest form to decentral exchanges, however their order books are stored on a central server they control and shown on their user interface (website). Other than the fact that they can re-order or censor the orders on their servers, there are other risks of front-running nature in these designs. Similarly 0xProtocol uses \textit{Relayers} which act as the orderbook holders and are not prune to cheating. One main issue with these exchanges is \textit{cancellation grief}. Although the orderbooks are not in the smart contract, in order to prevent denial of service attacks, user needs to send a transaction to cancel her order. In this case, when an adversarial actor sees the cancellation transaction, he sends a fill order transactions with higher gasPrice to get in front of the cancellation order and take the order before it is cancelled. As mentioned in ~\ref{minersfrontrunning}, miners are in a better control to perform such attack.

@@

Bancor is another Ethereum-based application that allows users to exchange their tokens without any counter-party risk. This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}-- ERC20 compatible tokens with a built-in liquidity mechanism that are always available to users. ERC20 is the interface standard for implementing tokens on top of Ethereum~\cite{erc20}. Smart Tokens can be bought and sold through the users smart contract at an automatically calculated price which displays supply and demand. Doing so, Bancor protocol provides continuous liquidity for digital assets without relying on an order book as there is no requirement to match sellers and buyers.
Recently, researchers have shown that Bancor is vulnerable to front running attacks. Implemented on the Ethereum blockchain, when Bancor transactions are broadcast to the network, they sit in a pending transaction pool known as \textit{mempool} waiting for the miners to mine them. Since Bancor handles all the trades and exchanges on the Ethereum blockchain (unlike other existing decentralized exchanges), these transactions are all visible to the public for 16s (the average Ethereum blocktime) before being included within a block. This leaves this blockchain-based decentralized exchange vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions and gain favorable profits~\cite{BancorIs7:online}. As mentioned in Section~\ref{sec:who can front-run?} and same as every other Ethereum based application, Bancor transactions can be front run by miners and other regular (non-miner) users. There is an implementation of a Bancor front running attack in the Python programming language which represent how a non-miner user can front run other network participants~\cite{NewTab13:online}.
%______________________________________________________________%
\subsection{Name Services.}

>>>>

\subsection{Blockchain Front-running} \label{sec:Front Running on the Blockchains}

% everything that has a line up , someone can jump in the line and front-run

@@

As mentioned in the Section~\ref{sec:intro}, for the purpose of this research we retrieved the top 25 DApps based on recent user activities from \texttt{DAppradar.com}\footnote{List of decentralized applications \url{https://dappradar.com/dapps}} in the first week of September 2018. We then categorize these applications into 4 principal groups of decentral applications (see Table~\ref{tab:top25dapps}). In this section, we take a deep look into one or two decentral applications from each category and pinpoint the technical details of front-running issue on each case. Although, no ICOs were spotted in the list at the time it was retrieved, we will thoroughly discuss our analysis on how ICOs are highly vulnerable to front-running activities (see Section~\ref{sec:ICOsfrontrunning}).

@@

%______________________________________________________________%
\subsection{Markets and Exchanges.} \label{sec:frontrunningExchanges}

% talk about velocity that seems to be not front-runnable but because of of the liquidity pool limitation, there can be an order that consumes the last chunk of liquidity "edge case" , to front run others and make their "option calls" fail

@@

Exchanges such as EtherDelta\footnote{also known as ForkDelta for the UI \url{https://forkdelta.app/}}, are closest implementation to decentral exchanges, however their order books are stored on a central server they control and shown on their user interface (website). Other than the fact that they can re-order or censor the orders on their servers, there are other risks of front-running nature in these designs. Similarly 0xProtocol~\cite{warren20170x} uses \textit{Relayers} which act as the orderbook holders and are not prune to cheating. One main issue with these designs is the \textit{cancellation grief}. Although the orderbooks are not in the smart contract, in order to prevent denial of service attacks, user needs to send a transaction to cancel her order. In this case, when an adversarial actor sees the cancellation transaction, he sends a fill order transactions with higher gasPrice to get in front of the cancellation order and take the order before it is cancelled. As mentioned in ~\ref{minersfrontrunning}, miners are in a better position to perform such attack.

@@

Bancor is another Ethereum-based application that allows users to exchange their tokens without any counter-party risk. This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}-- ERC20 compatible tokens with a built-in liquidity mechanism that are always available to users. ERC20 is the interface standard for implementing tokens on top of Ethereum~\cite{erc20}. Smart Tokens can be bought and sold through the users smart contract at an automatically calculated price which displays supply and demand. Doing so, Bancor protocol provides continuous liquidity for digital assets without relying on an order book as there is no requirement to match sellers and buyers.
Implemented on the Ethereum blockchain, when transactions are broadcast to the network, they sit in a pending transaction pool known as \textit{mempool} waiting for the miners to mine them. Since Bancor handles all the trades and exchanges on the Ethereum blockchain (unlike other existing decentralized exchanges), these transactions are all visible to the public for some time before being included within a block. This leaves this blockchain-based decentralized exchange vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions and gain favourable profits~\cite{BancorIs7:online}. Researchers have shown and implemented proof of concept code to front-run Banco as a regular non-miner user~\cite{NewTab13:online}.

%______________________________________________________________%
\subsection{Name Services.}
